Review stages

### 2024-07-03 doc/review-stages.qmd
docs: :memo: update review stages file with what we kept, etc

```{r setup}
#| include: false
library(tidyverse)
library(here)
library(fs)
targets::tar_config_set(store = here("_targets"))
```

@@

```{r tbl-title-disagreements}
#| tbl-cap: "Article titles **not** kept between all reviewers during the title screening stage."
targets::tar_read(titles_disagreed_on) |>
  select("Article titles" = title) |>
  knitr::kable()
```

@@

```{r tbl-abstracts-kept}
#| message: false
#| tbl-cap: "Number of articles each reviewer kept after the second screening of the abstracts."
targets::tar_read(abstracts_kept) |> 
  map(\(df) count(df, name = "Articles kept")) |>
  list_rbind(names_to = "Reviewers") |>
  # TODO: Include percent of total articles.
  knitr::kable()

# targets::tar_read(abstracts_kept) |> 
#   select("Article titles" = title) |>
#   knitr::kable()
```

>>>>

```{r setup}
#| include: false
library(tidyverse)
library(here)
library(fs)
targets::tar_config_set(store = here("_targets"))
source(here::here("R/abstract-review.R"))
```

@@

```{r tbl-titles-disagreements}
#| tbl-cap: "Article titles **not** kept between all reviewers during the title screening stage."
targets::tar_read(titles_disagreed_on) |>
  select("Article titles" = title) |>
  knitr::kable()
```

@@

```{r tbl-abstracts-kept}
#| message: false
#| tbl-cap: "Number of articles each reviewer kept after the second screening of the articles."
targets::tar_read(abstracts_kept) |> 
  map(\(df) count(df, name = "Articles kept")) |>
  list_rbind(names_to = "Reviewers") |>
  # TODO: Include percent of total articles.
  knitr::kable()
```

Based on the abstract review, we want to know how many of these titles
we all agreed on between the three reviewers:

```{r}
common_abstracts <- targets::tar_read(abstracts_agreed_on)
```

We seemed to agree on `r nrow(common_abstracts)` abstracts, with the
full article list shown in @tbl-abstracts-agreements.

```{r tbl-abstracts-agreements}
#| tbl-cap: !expr glue::glue("The {nrow(common_abstracts)} article abstracts we all agreed on and kept during the abstract screening stage.")
targets::tar_read(abstracts_agreed_on) |>
  select("Article titles" = title) |>
  knitr::kable()
```

```{r tbl-abstracts-disagreements}
#| tbl-cap: "Article abstracts **not** kept between all reviewers during the title screening stage."
targets::tar_read(abstracts_disagreed_on) |>
  select("Article titles" = title) |>
  knitr::kable()
```

Like with the title review, we saved a new csv file with all the
disagreements and then made a copy of that list in the file
`resolved.csv`. This file contains some articles that we disagreed on
but that were briefly reviewed by one reviewer, discussed, and included
in the end.

The abstracts we agreed on were:

```{r}
#| message: false
#| tbl-cap: "Article abstracts we agreed to keep from the disagreement list."
targets::tar_read(abstracts_resolved_path) |>
  read_abstract_yaml() |>
  select("Article title" = title) |>
  knitr::kable()
```

```{r}
#| message: false
#| tbl-cap: "Article abstracts we reviewed and selected to continue to final article reviewing."
targets::tar_read(abstracts_selected) |>
  select("Article title" = title) |>
  knitr::kable()
```
